The Legacy of the European Post-Master in Urbanism at TU Delft: A Text Mining Approach

### 2023-07-03 analysis/paper/paper.qmd

```{r get-pdf-text}
#| echo: false
#| cache: true

data_path <- here("analysis", "data", "derived_data", "emu_theses_with_text_and_location.csv")

if (!file.exists(data_path)) {
  # On the first run, this function might take extra time as a Python environment needs to be set up
  emu_theses$text <- convert_pdf_text(pdf_paths)

  # Write thesis dataframe to file
  write_csv(emu_theses, data_path)
} else {
  emu_theses$text <- read_csv(data_path)$text
  emu_theses$longitude <- read_csv(data_path)$longitude
  emu_theses$latitude <- read_csv(data_path)$latitude
}

@@

Similar to clustering on numeric data, topic modeling is a method of unsupervised classification of topics found in a group of documents [@silge2017].

@@

# We will use the Latent Dirichlet Allocation (LDA) algorithm for topic modeling
# In LDA, each document is a mixture of topics and each topic is a mixture of words
emu_theses_lda <- LDA(emu_theses_dtm, k = 2, control = list(seed = 2023))
emu_theses_lda

>>>>

```{r extract-pdf-text}
#| echo: false
#| cache: true

data_path <- here("analysis", "data", "derived_data", "emu_theses_with_text.csv")

if (!file.exists(data_path)) {
  # On the first run, this function might take extra time as a Python environment needs to be set up
  emu_theses$text <- convert_pdf_text(pdf_paths)
  write_csv(emu_theses, data_path)
} else {
  emu_theses$text <- read_csv(data_path)$text
}

@@

Similar to clustering on numeric data, topic modeling is a method of unsupervised classification of topics found in a group of documents [@silge2017]. We will use the Latent Dirichlet Allocation (LDA) algorithm for topic modeling. In LDA, each document is a mixture of topics and each topic is a mixture of words. The probability of a term being part of a topic is given by the beta statistic. The probability of a document being part of a topic is given by the gamma statistic.

@@

# Fit LDA model
emu_theses_lda <- LDA(emu_theses_dtm, k = 2, control = list(seed = 2023))
emu_theses_lda
